Long- and short-read metabarcoding technologies reveal similar spatio-temporal structures in fungal communities

### 2020-09-27 writing/transect_paper.Rmd
clean up alpha diversity plot

```{r alpha-compare, fig.scap = "(ref:alpha-compare-s)", fig.cap = "(ref:alpha-compare-s) (ref:alpha-compare)"}
ggpubr::ggarrange(
  remove_empty_facets(readd(alpha_plot_ASV)),
  remove_empty_facets(readd(alpha_plot_OTU)),
  ncol = 1,
  labels = "auto"
)
```

>>>>

```{r alpha-compare, fig.scap="(ref:alpha-compare-s)", fig.cap="(ref:alpha-compare-s) (ref:alpha-compare)", fig.height=8}
ggpubr::ggarrange(
  remove_empty_facets(readd(alpha_plot_ASV)),
  remove_empty_facets(readd(alpha_plot_OTU)),
  ncol = 1,
  labels = "auto",
  label.x = 0.9
)
```
